Respiratory vitdsteroids

### 2021-03-06 r_notebooks/preparing_differences/preparing_cortico_resp.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r cortico-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

cortico <- 
  read_rds("../data/presdata_updates_040121/presc_wales_cortico-resp.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  cortico_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
cortico_monthly_count_pre_cv19 <- 
  cortico_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

cortico_monthly_quantity_gp_pre_cv19 <- 
  cortico_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
cortico_monthly_count_pre_cv19 <- 
  cortico_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(cortico_monthly_count_pre_cv19)

cortico_monthly_quantity_gp_pre_cv19 <- 
  cortico_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(cortico_monthly_quantity_gp_pre_cv19)

@@

```{r, cortico-gp-practice-modelling}
plan(cluster)
system.time(cortico_gp_cv_models <-
  cortico_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

cortico_gp_cv_models %>%
  saveRDS("../data/cortico_gp_cv_models.rds")

cortico_gp_cv_models <- 
  read_rds("../data/cortico_gp_cv_models.rds")

cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r cortico-gp-modelling-accuracy}
best_model_gp <- 
  cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r cortico-gp-practice-forecasts}
plan(cluster)
system.time(cortico_gp_fcsts <-
              cortico_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

cortico_gp_fcsts %>%
  saveRDS("../data/cortico_gp_fcsts.rds")

cortico_gp_fcsts <- 
  read_rds("../data/cortico_gp_fcsts.rds")

@@

```{r, cortico-gp-practice-discrepancies}
best_model_gp <- 
  cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/cortico_discreps.rds")
```

>>>>

```{r cortico-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

cortico <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_cortico-resp.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  cortico_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
cortico_monthly_count_pre_cv19 <- 
  cortico_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

cortico_monthly_quantity_gp_pre_cv19 <- 
  cortico_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

## Replace missing values in training data
cortico_monthly_count_pre_cv19 <- 
  cortico_monthly_count_pre_cv19 %>% 
  model(arima = ARIMA(n)) %>%
  interpolate(cortico_monthly_count_pre_cv19)

cortico_monthly_quantity_gp_pre_cv19 <- 
  cortico_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(arima = ARIMA(n)) %>% 
  interpolate(cortico_monthly_quantity_gp_pre_cv19)

@@

```{r, cortico-gp-practice-modelling}
plan(cluster)
system.time(cortico_gp_cv_models <-
  cortico_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 36, step = 3))
plan(sequential)

cortico_gp_cv_models %>%
  saveRDS("../../data/cortico_gp_cv_models.rds")

cortico_gp_cv_models <- 
  read_rds("../../data/cortico_gp_cv_models.rds")

cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r cortico-gp-modelling-accuracy}
best_model_gp <- 
  cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r cortico-gp-practice-forecasts}
plan(cluster)
system.time(cortico_gp_fcsts <-
              cortico_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "8 months"))
plan(sequential)

cortico_gp_fcsts %>%
  saveRDS("../../data/cortico_gp_fcsts.rds")

cortico_gp_fcsts <- 
  read_rds("../../data/cortico_gp_fcsts.rds")

@@

```{r, cortico-gp-practice-discrepancies}
best_model_gp <- 
  cortico_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/cortico_discreps.rds")
```

### 2021-03-06 r_notebooks/preparing_differences/preparing_hcq.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r hcq-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

hcq <- 
  read_rds("../data/presdata_updates_040121/presc_wales_HCQ.rds") %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid)) %>% 
  janitor::clean_names()

@@

## Identify GPs with missing data 
gp_missing <- 
  hcq_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
hcq_monthly_count_pre_cv19 <- 
  hcq_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

hcq_monthly_quantity_gp_pre_cv19 <- 
  hcq_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
hcq_monthly_count_pre_cv19 <- 
  hcq_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(hcq_monthly_count_pre_cv19)

hcq_monthly_quantity_gp_pre_cv19 <- 
  hcq_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(hcq_monthly_quantity_gp_pre_cv19)

@@

```{r, hcq-gp-practice-modelling}
plan(cluster)
system.time(hcq_gp_cv_models <-
  hcq_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

hcq_gp_cv_models %>%
  saveRDS("../data/hcq_gp_cv_models.rds")

hcq_gp_cv_models <- 
  read_rds("../data/hcq_gp_cv_models.rds")

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r hcq-gp-modelling-accuracy}
best_model_gp <- 
  hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r hcq-gp-practice-forecasts}
plan(cluster)
system.time(hcq_gp_fcsts <-
              hcq_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

hcq_gp_fcsts %>%
  saveRDS("../data/hcq_gp_fcsts.rds")

hcq_gp_fcsts <- 
  read_rds("../data/hcq_gp_fcsts.rds")

@@

```{r, hcq-gp-practice-discrepancies}
best_model_gp <- 
  hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/hcq_discreps.rds")
```

>>>>

```{r hcq-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

hcq <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_HCQ.rds") %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid)) %>% 
  janitor::clean_names()

@@

## Identify GPs with missing data 
gp_missing <- 
  hcq_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
hcq_monthly_count_pre_cv19 <- 
  hcq_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

hcq_monthly_quantity_gp_pre_cv19 <- 
  hcq_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

## Replace missing values in training data
hcq_monthly_count_pre_cv19 <- 
  hcq_monthly_count_pre_cv19 %>% 
  model(arima = ARIMA(n)) %>%
  interpolate(hcq_monthly_count_pre_cv19)

hcq_monthly_quantity_gp_pre_cv19 <- 
  hcq_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(arima = ARIMA(n)) %>% 
  interpolate(hcq_monthly_quantity_gp_pre_cv19)

@@

```{r, hcq-gp-practice-modelling}
plan(cluster)
system.time(hcq_gp_cv_models <-
  hcq_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 36, step = 3))
plan(sequential)

hcq_gp_cv_models %>%
  saveRDS("../../data/hcq_gp_cv_models.rds")

hcq_gp_cv_models <- 
  read_rds("../../data/hcq_gp_cv_models.rds")

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r hcq-gp-modelling-accuracy}
best_model_gp <- 
  hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r hcq-gp-practice-forecasts}
plan(cluster)
system.time(hcq_gp_fcsts <-
              hcq_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "8 months"))
plan(sequential)

hcq_gp_fcsts %>%
  saveRDS("../../data/hcq_gp_fcsts.rds")

hcq_gp_fcsts <- 
  read_rds("../../data/hcq_gp_fcsts.rds")

@@

```{r, hcq-gp-practice-discrepancies}
best_model_gp <- 
  hcq_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/hcq_discreps.rds")
```

### 2021-03-06 r_notebooks/preparing_differences/preparing_paracet.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r paracet-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

paracet <- 
  read_rds("../data/presdata_updates_040121/presc_wales_paracetamol.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  paracet_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
paracet_monthly_count_pre_cv19 <- 
  paracet_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

paracet_monthly_quantity_gp_pre_cv19 <- 
  paracet_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
paracet_monthly_count_pre_cv19 <- 
  paracet_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(paracet_monthly_count_pre_cv19)

paracet_monthly_quantity_gp_pre_cv19 <- 
  paracet_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(paracet_monthly_quantity_gp_pre_cv19)

@@

```{r, paracet-gp-practice-modelling}
plan(cluster)
system.time(paracet_gp_cv_models <-
  paracet_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

paracet_gp_cv_models %>%
  saveRDS("../data/paracet_gp_cv_models.rds")

paracet_gp_cv_models <- 
  read_rds("../data/paracet_gp_cv_models.rds")

paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r paracet-gp-modelling-accuracy}
best_model_gp <- 
  paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r paracet-gp-practice-forecasts}
plan(cluster)
system.time(paracet_gp_fcsts <-
              paracet_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

paracet_gp_fcsts %>%
  saveRDS("../data/paracet_gp_fcsts.rds")

paracet_gp_fcsts <- 
  read_rds("../data/paracet_gp_fcsts.rds")

@@

```{r, paracet-gp-practice-discrepancies}
best_model_gp <- 
  paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/paracet_discreps.rds")

>>>>

```{r paracet-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

paracet <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_paracetamol.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  paracet_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
paracet_monthly_count_pre_cv19 <- 
  paracet_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

paracet_monthly_quantity_gp_pre_cv19 <- 
  paracet_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

## Replace missing values in training data
paracet_monthly_count_pre_cv19 <- 
  paracet_monthly_count_pre_cv19 %>% 
  model(arima = ARIMA(n)) %>%
  interpolate(paracet_monthly_count_pre_cv19)

paracet_monthly_quantity_gp_pre_cv19 <- 
  paracet_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(arima = ARIMA(n)) %>% 
  interpolate(paracet_monthly_quantity_gp_pre_cv19)

@@

```{r, paracet-gp-practice-modelling}
plan(cluster)
system.time(paracet_gp_cv_models <-
  paracet_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 36, step = 3))
plan(sequential)

paracet_gp_cv_models %>%
  saveRDS("../../data/paracet_gp_cv_models.rds")

paracet_gp_cv_models <- 
  read_rds("../../data/paracet_gp_cv_models.rds")

paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r paracet-gp-modelling-accuracy}
best_model_gp <- 
  paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r paracet-gp-practice-forecasts}
plan(cluster)
system.time(paracet_gp_fcsts <-
              paracet_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "8 months"))
plan(sequential)

paracet_gp_fcsts %>%
  saveRDS("../../data/paracet_gp_fcsts.rds")

paracet_gp_fcsts <- 
  read_rds("../../data/paracet_gp_fcsts.rds")

@@

```{r, paracet-gp-practice-discrepancies}
best_model_gp <- 
  paracet_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/paracet_discreps.rds")

### 2021-03-06 r_notebooks/preparing_differences/preparing_vitd.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r vitd-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

vitd <- 
  read_rds("../data/presdata_updates_040121/presc_wales_vitamind.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  vitd_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
vitd_monthly_count_pre_cv19 <- 
  vitd_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

vitd_monthly_quantity_gp_pre_cv19 <- 
  vitd_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
vitd_monthly_count_pre_cv19 <- 
  vitd_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(vitd_monthly_count_pre_cv19)

vitd_monthly_quantity_gp_pre_cv19 <- 
  vitd_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(vitd_monthly_quantity_gp_pre_cv19)

@@

```{r, vitd-gp-practice-modelling}
plan(cluster)
system.time(vitd_gp_cv_models <-
  vitd_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

vitd_gp_cv_models %>%
  saveRDS("../data/vitd_gp_cv_models.rds")

vitd_gp_cv_models <- 
  read_rds("../data/vitd_gp_cv_models.rds")

vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r vitd-gp-modelling-accuracy}
best_model_gp <- 
  vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r vitd-gp-practice-forecasts}
plan(cluster)
system.time(vitd_gp_fcsts <-
              vitd_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

vitd_gp_fcsts %>%
  saveRDS("../data/vitd_gp_fcsts.rds")

vitd_gp_fcsts <- 
  read_rds("../data/vitd_gp_fcsts.rds")

@@

```{r, vitd-gp-practice-discrepancies}
best_model_gp <- 
  vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/vitd_discreps.rds")

>>>>

```{r vitd-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

vitd <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_vitamind.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  vitd_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
vitd_monthly_count_pre_cv19 <- 
  vitd_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

vitd_monthly_quantity_gp_pre_cv19 <- 
  vitd_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

## Replace missing values in training data
vitd_monthly_count_pre_cv19 <- 
  vitd_monthly_count_pre_cv19 %>% 
  model(arima = ARIMA(n)) %>%
  interpolate(vitd_monthly_count_pre_cv19)

vitd_monthly_quantity_gp_pre_cv19 <- 
  vitd_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(arima = ARIMA(n)) %>% 
  interpolate(vitd_monthly_quantity_gp_pre_cv19)

@@

```{r, vitd-gp-practice-modelling}
plan(cluster)
system.time(vitd_gp_cv_models <-
  vitd_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 36, step = 3))
plan(sequential)

vitd_gp_cv_models %>%
  saveRDS("../../data/vitd_gp_cv_models.rds")

vitd_gp_cv_models <- 
  read_rds("../../data/vitd_gp_cv_models.rds")

vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r vitd-gp-modelling-accuracy}
best_model_gp <- 
  vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r vitd-gp-practice-forecasts}
plan(cluster)
system.time(vitd_gp_fcsts <-
              vitd_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "8 months"))
plan(sequential)

vitd_gp_fcsts %>%
  saveRDS("../../data/vitd_gp_fcsts.rds")

vitd_gp_fcsts <- 
  read_rds("../../data/vitd_gp_fcsts.rds")

@@

```{r, vitd-gp-practice-discrepancies}
best_model_gp <- 
  vitd_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/vitd_discreps.rds")
